Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Add missing comma.

In this paper we will describe an implementation of the Raft protocol
in a browser context using WebRTC as the communication channel. We
will describe the results of the implementation and look at some of
unique challenges (and opportunities) we encountered with the
implementation. We will also explore some ideas for further study.

\section{Motivation/Use Cases}
The traditional use of distributed consensus is in the data-center
(private or cloud based) often as the core coordination component
of a replicated data-storage system. %TODO/CITE
In these examples, the set of nodes that compose the cluster tend to
be fairly static and changes to cluster membership are usually for the
purpose of replacing nodes. Changes to the long-term size of the
cluster are uncommon. %TODO/CITE

>>>>

In this paper we will describe an implementation of the Raft protocol
in a browser context using WebRTC as the communication channel. We
will describe the results of the implementation and look at some of
the unique challenges (and opportunities) we encountered with the
implementation. We will also explore some ideas for further study.

\section{Motivation/Use Cases}
The traditional use of distributed consensus is in the data-center
(private or cloud based), often as the core coordination component
of a replicated data-storage system. %TODO/CITE
In these examples, the set of nodes that compose the cluster tend to
be fairly static and changes to cluster membership are usually for the
purpose of replacing nodes. Changes to the long-term size of the
cluster are uncommon. %TODO/CITE
